%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer - Limits and Trading Controls $\;\bullet\;$ C++} % Job title
    {Bloomberg} % Organization
    {New York City, NY (Remote)} % Location
    {Jan. 2021 - Apr - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented and helped design a parallel evaluation pipeline for trade compliance checks.}
      \item {Decreased latency and significantly improved throughput of a system performing hundreds of millions of compliance evaluations daily.}
      \item {Produced fully lock-free and unit-tested code; profiled and optimized to obtain better performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer $\;\bullet\;$ Python, C\#, MySQL, Azure} % Job title
    {IvyGlobal} % Organization
    {Palo Alto, CA (Remote)} % Location
    {Jul. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a pipeline to query, clean, and format training data; collaborated with Riiid to build an AI test prep platform.}
      \item {Integrated exam-taking and score-reporting services while adding powerful analytics tools for instructors.}
      \item {Developed dynamic admin pages to visualize usage patterns and redesigned many frontend components.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Distributed Systems \& Big Data $\;\bullet\;$ Java} % Job title
    {Yahoo!} % Organization
    {Sunnyvale, CA} % Location
    {Jan. 2021 - Apr - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Canceled due to COVID-19}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Full Stack Developer $\;\bullet\;$ PHP, VueJS, MySQL, AWS, ElasticSearch} % Job title
    {Jasper PIM} % Organization
    {Toronto, ON} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Parallelized and optimized backend batch processing resulting in an overall 1000x performance increase.}
      \item {Revived advanced search by fixing critical indexing bug, worked directly with clients to implement custom features.}
      \item {Redesigned asset architecture to generate signed URL's and upload direct to S3, contributing to a stateless server.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
