%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Select Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvprojectentry
    {\href{https://www.github.com/RileyJackson2000/fluffy-computing-machine}{{3d Physics Engine }\faGithubSquare\acvHeaderIconSep}} % Organization/group
    {C++, OpenGL, Eigen, gtest} % Location
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Designed and developed a constraint-based rigid body simulator with support for joints, springs, and (Coulomb) friction.}
      \item {Implemented a mathematical optimization library with support for linear, quadratic, and linear complementary problems.}
      \item {Something about GPU shaders, lighting model.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {\href{https://www.github.com/RileyJackson2000/tsp_art}{{Travelling Salesman Art }\faGithubSquare\acvHeaderIconSep}} % Organization/group
    {C++, OpenGL, Cairo} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Designed a rendering engine which which takes any image and redraws it with a single line.}
      \item {Solves the travelling salesman problem on a graph obtained by stippling an image, then renders the result into art.}
      \item {Adapted and improved upon the algorithm in R. Bridson's paper ``Fast Poisson Disk Sampling in Arbitrary Dimensions''.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {Robotics} % Organization/group
    {C++, SolidWorks} % Location
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Captain of Team Canada robotics, competed in the 2017 ROBOCUP World Championship in Nagoya, Japan (4-3 record).}
      \item {Responsible for all programming and managed a team of 4 peers to oversee the construction of a soccer playing robot.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {\href{http://rjackson2000.com/\#vir}{Vir \faGithubSquare\acvHeaderIconSep}} % Organization/group
    {C++, NCurses} % Location
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Created a vim-esque terminal editor supporting modal editing, linear undo, file i/o, vim-tabs, command chaining, etc.}
      \item {Implemented C/C++ syntax highlighting; supports (contextual) keywords, identifiers, numeric literals, etc.}
      \item {Developed within 3 weeks with a strict adherence to modern C++ best practices and design patterns.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
